Matching Bullets

### 2015-12-10 imaging-paper.Rnw
Disclaimer on website

The ``smoothing factor" described in the algorithm represents the window size to use for a rolling average. Higher values of the smoothing factor therefore lead to more smoothed results. In the groove detection portion of this algorithm, we wish to remove most of the deviation but still maintain enough signal in the groove to detect it. Empirically, a value of 35 for the smoothing factor seems to work quite well. It is important to note that the smoothing pass is done twice. That is, the smoothed data is once again smoothed by computing a new rolling average with the same smoothing factor. This bears some similarities to the ideas of John Tukey in his book Exploratory Data Analysis, where he describes a smoothing process called ``twicing" in which a second pass is made on the residuals computed from the first pass and then added back to the result \cite{tukey:1977}. This has the effect of introducing a little bit more variance into the smoothed data. We instead performed a second smoothing pass on the smoothed data, which has the effect of weighting observations near the center highest, while the weights linearly drop off as you reach the end of the smoothing window or smoothing factor.

@@

The application includes a button which allows the automatic creation of a residual plot from the Loess fits of two bullets. An x coordinate value can be selected, and a cross-section of the two bullet at the x value will be taken. The previously described Loess regression procedure will be applied to the two cross sections. A residual plot will be produced beneath the surface plots allowing for an assessment of the similarity of the markings. It is intended that users will perform this procedure at different x values in order to see whether the markings indicate a match at different points along the bullet.

>>>>

The ``smoothing factor" described in the algorithm represents the window size to use for a rolling average. Higher values of the smoothing factor therefore lead to more smoothed results. In the groove detection portion of this algorithm, we wish to remove most of the deviation but still maintain enough signal in the groove to detect it. Empirically, a value of 35 for the smoothing factor seems to work quite well (later in the manuscript we investigate varying the smoothing factor). It is important to note that the smoothing pass is done twice. That is, the smoothed data is once again smoothed by computing a new rolling average with the same smoothing factor. This bears some similarities to the ideas of John Tukey in his book Exploratory Data Analysis, where he describes a smoothing process called ``twicing" in which a second pass is made on the residuals computed from the first pass and then added back to the result \cite{tukey:1977}. This has the effect of introducing a little bit more variance into the smoothed data. We instead performed a second smoothing pass on the smoothed data, which has the effect of weighting observations near the center highest, while the weights linearly drop off as you reach the end of the smoothing window or smoothing factor.

@@

The application includes a button which allows the automatic creation of a residual plot from the Loess fits of two bullets. An x coordinate value can be selected as a cross cut, and a cross-section of the two bullet at the x value will be taken. The previously described Loess regression procedure will be applied to the two cross sections. A residual plot will be produced beneath the surface plots allowing for an assessment of the similarity of the markings. It is intended that users will perform this procedure at different x values in order to see whether the markings indicate a match at different points along the bullet.

Enhancements to the web application are still in progress. In particular, much of the automatic matching functionality described in the next section will be added in the future.
